---
name: Camila Farias Amorim
position: "Postdoctoral Researcher in Immunology and Computational Biology"
address: "University of Pennsylvania, Department of Pathobiology, School of Veterinary Medicine"
phone: +1 215.594.9806
email: "camilafarias112@gmail.com"
twitter: amorim_cfa
github: camilafarias112
www: camilafarias112.github.io
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 414141
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```


# Education and training

```{r degrees, results='asis'}
library(tibble)
tribble(
  ~ degree, ~ uni, ~ loc, ~ dates, #~ details,
  "Postdoctoral researcher", "University of Pennsylvania", "Philadelphia, PA, USA", "2018-current",
  "Ph.D fellow in Bioinformatics", "University of Pennsylvania", "Philadelphia, PA, USA", "2017",
  "Ph.D. in Immunology and Health Sciences", "Federal University of Bahia", "Salvador, BA, Brazil", "2014 - 2017",
  "Masters in Immunology and Health Sciences", "Federal University of Bahia", "Salvador, BA, Brazil", "2012 - 2013",
  "B.S. in Biomedical Sciences", "Federal University of Bahia", "Salvador, BA, Brazil", "2008 - 2011"
  
) %>% 
  detailed_entries(uni, dates, degree, loc)
```

# Skills in Computational Biology/Bioinformatics
* **Next-generation sequencing platforms**  
Bulk RNA-seq  
Single-cell RNA-seq (scRNA-seq) 
Microbial 16S-sequencing
* **Managing and processing next-generation sequencing data**  
BLAST  
Shell scripting  
Alignment/mapping to reference genomes and transcriptomes with *TopHat*, *Star*, *Kallisto*, *Bowtie2*  
Ensembl  
Metadata quality control (QC) with *FastQC* and *multiQC*  
* **Next-generation sequencing data analysis**  
Omics analysis in R/RStudio with *Bioconductor* packages  
Ensembl-associated packages (*BiomaRt*, *ensembldb*, *tximports*, *Biostrings*, etc.)  
Principal component analysis (PCA) and dimensionality reduction (t-SNE and UMAP)   
Differential expression analysis (*DESeq2*, *limma*, *edgeR*, etc.) and module identification with weighted correlation network analysis (*WGCNA*)  
Functional enrichment analysis (networks with *Cytoscape*, Gene Ontology using *DAVID*, GSEA - MSigDB from Broad Institute, *GSVA* and *GSEAbase* packages)  
Cell subset estimation in bulk RNA-seq datasets with *ImmQuant and CIBERSORTx*  
scRNA-seq analysis and data mining with *Seurat* and *SingleCellExperiment*, *monocle* pseudotime analysis  
* **Data vizualization**  
Experienced in data mining and plotting with *tidyverse* tools    
VennDiagram, heatmaps, ROC analysis, etc.   
* **Data reproducibility, transparency and public data acession**  
notebooks  
markdown (.md)  
Rmarkdown (.Rmd) and *knitr*  
Interactive data reports and *shinny apps*  
Gene Expression Omnibus (GEO) from NCBI  
* **Statistical tools, programming languages and operating systems**  
R (experienced)  
Python (beginner)  
MAC OS  
Linux  
Windows  

# Skills in Biology, Immunology and Health Sciences
* **keywords**: immunology, genetics/omics, parasitism, microbiology, virology, cell biology
* Culture of parasites (*Leishmania spp.*, *Toxoplasma gondii*)
* Clinical experience in endemic fields of infectious tropical diseases
* Contact with human patients and experience with biological sample collection (blood draw, skin biopsies, swabs)
* Wet lab technics: primary cell and cell lineage culture, qPCR, ELISA, flow cytometry, optical microscopy, DNA and RNA extraction, cDNA library preparation, *Illumina* protocols for high-throughput sequencing

# CodeOcean capsules
* **Variable gene expression and parasite load predict treatment outcome in cutaneous leishmaniasis**. Amorim CF, Novais FO, Nguyen B, Misic AM, Carvalho LP, Carvalho EM, Beiting DP, Scott P. *DOI:* **[\textcolor{red}{10.24433/CO.5903311.v1}](https://doi.org/10.24433/CO.5903311.v1)**   

* **DIYtranscriptomics**. Alexander S. F. Berry, Camila Farias Amorim, Corbett T. Berry, Elizabeth D. English, Daniel P. Beiting. *DOI:* **[\textcolor{red}{10.24433/CO.8082955.v1}](https://doi.org/10.24433/CO.8082955.v1)**  

# Publications (peer-reviewed)

**[\textcolor{red}{Google Scholar Profile}](https://scholar.google.com/citations?hl=en&user=6jg00_wAAAAJ)**

```{r publications}
library(scholar)
scholar::get_publications("6jg00_wAAAAJ") %>%
  arrange(desc(year)) %>%
  detailed_entries(
    what = author,
    when = year,
    with = title,
    where = journal
  )
```

# Teaching

```{r}
tribble(
  ~ title, ~ year,
  "Next-generation sequencing and transcriptomics analysis using the R programming language - Teaching assistant", "2018-current",
) %>%
  brief_entries(title, year)
```
*Description of the role*: Teaching - hands on - professionals in the biology field to analyze their own Next-generation sequencing datasets. Support in planning the study design and interpretation of the data from a biology background.  

**[\textcolor{red}{DIYtranscriptomics.com}](http://diytranscriptomics.com/)**  

# Additional position
```{r position, results='asis'}
library(tibble)
tribble(
  ~ degree, ~ uni, ~ loc, ~ dates, #~ details,
  "Postdoctoral researcher in the Center for Host-Microbial Interactions (CHMI) for sequencing and Omics analysis (shared position)", "University of Pennsylvania", "Philadelphia, PA, USA", "2017-current",
) %>% 
  detailed_entries(degree, dates, uni, loc)
```
**[\textcolor{red}{CHMI - hostmicrobe.org}](http://hostmicrobe.org/)**

# Awards & Achievements

```{r}
tribble(
  ~ award, ~ year,
  "Ph.D fellow scholarship award to develop a scientific research project abroad - by Coordenação de Aperfeiçoamento de Pessoal de Nível Superior (CAPES, Brazil)", "2017",
) %>%
  brief_entries(award, year)
```

# Invited and selected talks

* *Parasite load and host cytotoxicity-related gene expression are potential biomarkers for treatment outcome*. American Society of Tropical Medicine and Hygiene (ASTMH) Meeting. Maryland, USA. November 23, 2019.

* *Predicting Treatment Failure in Cutaneous Leishmaniasis*. Tropical Medicine Research Center (TMRC) Meeting. Salvador, Bahia, Brazil. March 12, 2019.

* *Predicting Treatment Failure in Cutaneous Leishmaniasis*. 22 and 23th Annual Woods Hole Immunoparasitology Conference. Woods Hole, MA, USA, May 2018.

* *NK cells citotoxicity is impaired in HAM/TSP patients*. XII International Symposium of HTLV in Brazil and IV Paulista Symposium of HTLV. São Paulo, Brazil, 2016.

* *The role of viral factors on monocytes/macrophages activation and function in HTLV-1 infection*. XXXIX Congress of the Brazilian Society of Immunology. São Paulo, Brazil, 2014.

# PrePrint Reviews

* *Links between environment, diet, and the hunter-gatherer microbiome*. 2018 **[\textcolor{red}{PREreview}](https://prereview.org/users/237518/articles/308580-prereview-journal-club-links-between-environment-diet-and-the-hunter-gatherer-microbiome)** 

# Languages
* Portuguese (native)
* English
* Spanish



